### 2019-01-03 Paper1/ProofOneShotIPM.tex
switched one-shot IPM scheme

&\bm{\lambda}_{j}^{n} =  \bm{d}(\bm{u}_j^{n},\bm{\lambda}_j^{n-1}) \enskip \text{ for all j} \label{eq:oneshotIPMdual}\\
&\bm{u}_j^{n+1} =  \bm{c}\left(\bm{\lambda}_{j-1}^n,\bm{\lambda}_{j}^n,\bm{\lambda}_{j+1}^n\right)\label{eq:oneshotIPMmoment}.

@@

Now we begin to derive the spectrum of the \textit{One-Shot IPM} iteration \eqref{eq:oneshotIPM}. To obtain a single iteration function, we plug the dual iteration step \eqref{eq:oneshotIPMdual} into the moment iteration \eqref{eq:oneshotIPMmoment} to obtain

@@

\bm{u}_j^{n+1} =  \bm{c}\left(\bm{d}(\bm{u}_{j-1}^{n},\bm{\lambda}_{j-1}^{n-1}),\bm{d}(\bm{u}_{j}^{n},\bm{\lambda}_{j}^{n-1}),\bm{d}(\bm{u}_{j+1}^{n},\bm{\lambda}_{j+1}^{n-1})\right)

@@

@@

\end{document}

>>>>

&\bm{u}_j^{n+1} =  \bm{c}\left(\bm{\lambda}_{j-1}^n,\bm{\lambda}_{j}^n,\bm{\lambda}_{j+1}^n\right)\label{eq:oneshotIPMmoment}\\
&\bm{\lambda}_{j}^{n+1} =  \bm{d}(\bm{u}_j^{n+1},\bm{\lambda}_j^{n}). \label{eq:oneshotIPMdual}

@@

Now we begin to derive the spectrum of the \textit{One-Shot IPM} iteration \eqref{eq:oneshotIPM}. To obtain a single iteration function, we plug the moment iteration step \eqref{eq:oneshotIPMmoment} into the dual iteration \eqref{eq:oneshotIPMdual} to obtain

@@

\bm{\lambda}_j^{n+1} =  \bm{d}\left( \bm{c}\left(\bm{\lambda}_{j-1}^n,\bm{\lambda}_{j}^n,\bm{\lambda}_{j+1}^n\right),\bm{\lambda}_j^n \right)

@@

The 
\qed

@@

We can first update the dual and then the moment vector:
\begin{subequations}\label{eq:oneshotIPMvv}
\begin{align}
&\bm{\lambda}_{j}^{n} =  \bm{d}(\bm{u}_j^{n},\bm{\lambda}_j^{n-1}) \enskip \text{ for all j} \label{eq:oneshotIPMdualvv}\\
&\bm{u}_j^{n+1} =  \bm{c}\left(\bm{\lambda}_{j-1}^n,\bm{\lambda}_{j}^n,\bm{\lambda}_{j+1}^n\right)\label{eq:oneshotIPMmomentvv}.
\end{align}
\end{subequations}
In the following, we prove convergence of this scheme:
\begin{theorem}
The \textit{One-Shot IPM} scheme \eqref{eq:oneshotIPM} converges with the same rate as the moment iteration \eqref{eq:momentIteration} if the preconditioner $\bm{B} = \langle u'(\bm{\varphi}^T\bm{\lambda}_j^{n-1})\bm{\varphi}\bm{\varphi}^T\rangle$ is used.
\end{theorem}
\begin{proof}
Now we begin to derive the spectrum of the \textit{One-Shot IPM} iteration \eqref{eq:oneshotIPM}. To obtain a single iteration function, we plug the dual iteration step \eqref{eq:oneshotIPMdual} into the moment iteration \eqref{eq:oneshotIPMmoment} to obtain
\begin{align*}
\bm{u}_j^{n+1} =  \bm{c}\left(\bm{d}(\bm{u}_{j-1}^{n},\bm{\lambda}_{j-1}^{n-1}),\bm{d}(\bm{u}_{j}^{n},\bm{\lambda}_{j}^{n-1}),\bm{d}(\bm{u}_{j+1}^{n},\bm{\lambda}_{j+1}^{n-1})\right)
\end{align*}
The 
\end{proof}
\end{document}
